Using simulation to optimize the sampling design of fisheries-independent trawl surveys

### 2019-05-21 analysis/paper/sim_survey_paper.Rmd
Start revising the discussion

Once the survey data are simulated, they then need to be analyzed to obtain an index of abundance. While there are many model-based options for obtaining an index (**TODO: add references**), survey-based approaches, such as stratified analyses, are often used. Here we apply formula presented in Smith and Somerton [-@Smith1981] to calculate stratified estimates of total abundance ($\hat{I}_{y,k}$), abundance at length ($\hat{I}_{l,y,k}$) and abundance at age ($\hat{I}_{a,y,k}$). Note that estimates of total abundance are based on aggregate catch while abundance at length requires length frequencies to be bumped up using set-specific ratios of measured to caught fish, and these length frequencies are converted to age by applying a division-level age-length-key. We used root-mean-squared error (RMSE) as a measure of the precision and bias of the abundance at age estimates from each survey:

@@

>>>>

Once the survey data are simulated, they then need to be analyzed to obtain an index of abundance. While there are many model-based options for obtaining an index [e.g. @Thorson2015], survey-based approaches, such as stratified analyses, are often used. Here we apply formula presented in Smith and Somerton [-@Smith1981] to calculate stratified estimates of total abundance ($\hat{I}_{y,k}$), abundance at length ($\hat{I}_{l,y,k}$) and abundance at age ($\hat{I}_{a,y,k}$). Note that estimates of total abundance are based on aggregate catch while abundance at length requires length frequencies to be bumped up using set-specific ratios of measured to caught fish, and these length frequencies are converted to age by applying a division-level age-length-key. We used root-mean-squared error (RMSE) as a measure of the precision and bias of the abundance at age estimates from each survey:

@@

While there are several simulation frameworks for testing the design of fisheries-independent trawl surveys [e.g. @puerta2019; @schnute2003], there are few tools that facilitate such work. Here we document an R package with a series of functions for testing the multi-layred sampling design of spatial, age-structured populations. The package can also serve as a medium for the simulation testing of methods for analyzing such data. "Good survey design is a crucial prerequisite for obtaining reliable results" [@thomas2010]...
